The Effect of Media Frames on Issue Attitudes

### 2021-10-04 paper/main.tex

These highly parallel trends might raise another problem, however. Possibly, no significant variation of reader groups' migration opinion from the general trend can be observed. To address this concern, I estimate DiDs for all wave-issue-paper combinations. This means I use attitudinal questions on all political issues included in the GLES Panel (economic, issues, climate, ...), and assess whether news consumption matters for opinion formation more generally. The upper panel of figure \ref{fig:p_values} shows the distribution of p-values for the DiD-term from 1,752 fixed-effect models with GLES Panel data. The distribution shows a considerable deviation from the expected uniform distribution (visible in the lower panel) were there no explaining variation in the DiD-term beyond the uniform effects of wave and paper readership. This means, more often than random (12\% vs 5\%), the opinions of consumers of certain news deviate from the opinions of other citizens. This is even more severe for the 192 wave-paper combinations concerning the immigration or integration item used in the remainder of this study, where 18\% of all estimated DiDs fall under the 5\%-threshold\footnote{See plot in appendix \ref{}}.  This strongly indicates that news consumption matters for opinion formation and that the data shows variation which can be explained, despite highly parallel trends.

\subsection{Correlation of DiD with frame prevalence}
% show correlation of DiD with prevalence of media frames (STM)
\begin{figure}[!ht]
    \centering
    \includegraphics[width=\textwidth]{paper/vis/effectplot_frames_did.png}
    \caption{Correlation of opinion shifts (DiDs) with media attention or shifts in attention (DiD's) for different specifications.}
    \label{fig:did_corr}
\end{figure}

@@

This is however not the case. As figure \ref{fig:did_corr} shows, even with different specifications, \textit{no} estimate has predictive power for our analysis. For example, in the upper left panel 'crime', we can see 5 different lags 'g', '6m', '1m', '1w', '1d' distinguished vertically, and the effects for two different issues in the two different panes. Additionally, the color of the points indicates whether the model was estimated only for readers of a single newspaper (lower N, but no treatment diffusion) or all readers of a newspaper (who might read another newspaper, say SZ readers who also read FAZ). All estimates are clearly clustering around the null, indicating no effect. While the 'exclusive reader' estimates show more variation, they also indicate far broader confidence intervals. There is no considerable difference across lags, and the variables only differ by the broader confidence intervals of the integration variable, owing to the fewer waves including this question. Generally, this analysis indicates no effect of media framing of migration on migration attitudes.

@@

>>>>

These highly parallel trends might raise another problem, however. Possibly, no significant variation of reader groups' migration opinion from the general trend can be observed. To address this concern, I estimate DiDs for all wave-issue-paper combinations. This means I use attitudinal questions on all political issues included in the GLES Panel (economic, issues, climate, ...), and assess whether news consumption matters for opinion formation more generally. The upper panel of figure \ref{fig:p_values} shows the distribution of p-values for the DiD-term from 1,752 fixed-effect models with GLES Panel data. The distribution shows a considerable deviation from the expected uniform distribution (visible in the lower panel) were there no explaining variation in the DiD-term beyond the uniform effects of wave and paper readership. This means, more often than random (12\% vs 5\%), the opinions of consumers of certain news deviate from the opinions of other citizens. This is even more severe for the 192 wave-paper combinations concerning the immigration or integration item used in the remainder of this study, where 18\% of all estimated DiDs fall under the 5\%-threshold\footnote{See plot in appendix \ref{app:p-val_imm}}.  This strongly indicates that news consumption matters for opinion formation and that the data shows variation which can be explained, despite highly parallel trends.

\subsection{Correlation of DiD with frame prevalence}

\begin{figure}[!ht]
    \centering
    \includegraphics[width=\textwidth]{paper/vis/effectplot_frames_did.png}
    \caption{Correlation of opinion shifts (DiDs) with media attention or shifts in attention (DiD's) for different specifications.}
    \label{fig:did_corr}
\end{figure}

@@

This is however not the case. As figure \ref{fig:did_corr} shows, even with different specifications, \textit{no} estimate has predictive power for our analysis. For example, in the upper left panel 'crime', we can see four different lags indicating the frame prevalence of the past day, week, month, or half year (up to the last survey date) distinguished vertically, and the effects for two different issues in the two different panes. Additionally, the color of the points indicates whether the model was estimated only for readers of a single newspaper (lower N, but no treatment diffusion) or all readers of a newspaper (who might read another newspaper, say SZ readers who also read FAZ). All estimates are clearly clustering around the null, indicating no effect. While the 'exclusive reader' estimates show more variation, they also indicate far broader confidence intervals. There is no considerable difference across lags, and the variables only differ by the broader confidence intervals of the integration variable, owing to the fewer waves including this question. Generally, this analysis indicates no effect of media framing of migration on migration attitudes.

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=\textwidth]{paper/vis/DiD_model_ps_immint.png}
    \caption{Empirical and theoretical p-values of 192 DiD-models corresponding to the immigration and integration questions of the GLES.}
    \label{fig:my_label}
\end{figure}
